interpolation

### 2023-11-21 interpolation.Rmd
Update interpolation.Rmd

>>>>

This document shows the process for determining whether interpolation for drift 20 was appropriate
during the 4 days the GPS went dark. I compare environmental variables of interpolated points to
those at the start and end of the gap. Since the interpolated environmental variables are significantly
different, it's advised to eliminate them from environmental analysis.
